\LARGE \bf Mixed Non-Bayesian and DeGroot Learning

### 2012-12-12 docs/paper.tex
Math is hard!
A couple of typos.

We can see this process in more detail in Figure~\ref{fig:dg_faster}, which shows the average beliefs in $\theta^*$ for the intial steps of two trials on a complete graph. It is clear that the DeGroot nodes essentially act as amplifiers, magnifying the initial belief updates of the Non-Bayesian nodes. This will in turn strengthen the Non-Bayesian nodes beliefs in $\theta^*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates. This feedback cycle increases the speed of convergence.

@@

The results, presented in Figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph. Additionally, we can see that the complete graph takes longer to converge than the other graph types. This seems counter-intuitive at first: wouldn't a complete graph diffuse information more quickly, and threfore decrease the convergence time? The answer is that a complete graph has a large ``inertia''. To see that, imagine a graph comprised entirely of Non-Bayesian nodes that is trying to distinguish between two distributions $m_1$ and $m_2$. Let's say that node $i$ is the first one to receive a signal, and suppose that after the Bayesian update node $i$'s belief in $m_1$ is $p$. For the sake of concreteness, assume that $a_{ij}=1/(n+1)$ where $n$ is the number of node $i$'s neighbors. Then by Equation~\ref{eq:non_bayesian_update}:

\begin{equation*}
\mu_{i,t+1}(\theta_1) = \frac{p}{n+1} + \frac{n}{n+1}\left(\frac{1}{2}\right) = \frac{2p + n}{2n + 1} 
\end{equation*}

>>>>

We can see this process in more detail in Figure~\ref{fig:dg_faster}, which shows the average beliefs in $\theta^*$ for the initial steps of two trials on a complete graph. It is clear that the DeGroot nodes essentially act as amplifiers, magnifying the initial belief updates of the Non-Bayesian nodes. This will in turn strengthen the Non-Bayesian nodes beliefs in $\theta^*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates. This feedback cycle increases the speed of convergence.

@@

The results, presented in Figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph. Additionally, we can see that the complete graph takes longer to converge than the other graph types. This seems counter-intuitive at first: wouldn't a complete graph diffuse information more quickly, and therefore decrease the convergence time? The answer is that a complete graph has a large ``inertia''. To see that, imagine a graph comprised entirely of Non-Bayesian nodes that is trying to distinguish between two distributions $m_1$ and $m_2$. Let's say that node $i$ is the first one to receive a signal, and suppose that after the Bayesian update node $i$'s belief in $m_1$ is $p$. For the sake of concreteness, assume that $a_{ij}=1/(n+1)$ where $n$ is the number of node $i$'s neighbors. Then by Equation~\ref{eq:non_bayesian_update}:

\begin{equation*}
\mu_{i,t+1}(\theta_1) = \frac{p}{n+1} + \frac{n}{n+1}\left(\frac{1}{2}\right) = \frac{2p + n}{2n + 2} 
\end{equation*}
